---
title: "Read COH data"
author: "Alan Jackson"
date: "January 5, 2020"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)

path <- "/home/ajackson/Rprojects/Geocoding/"

knitr::opts_chunk$set(echo = TRUE)
```

## Read in csv file

```{r read in file}

DF <- read_csv(paste0(path, "COH_ADDRESS_POINTS__PDD.csv"),
               col_types = "dddddcccccccccccddccccccccccccccc")

```

##  Do some cleanup and recast some variables

a handful of zipcodes end in *
several addresses contain a letter at the end like "B"
etc

```{r look at data}

check_num <- function(name_a, a){paste("Range", name_a, toString(range(a, na.rm=TRUE), sep=", "), "number of NA's", sum(is.na(a)))}

check_char <- function(name_a, a){print(paste("Variable:", name_a))
  print(head(unique(a), 25))
  print(paste("Number of NA's:", sum(is.na(a))))
  print(paste("Number Unique:", length(unique(a))))}

check_notnum <- function(name_a, a){print(paste("Variable:", name_a, "non-numerics =", length(a[grepl("\\D",a)])))
  head(a[grepl("\\D",a)])
  }

check_num("X", DF$X)
print("-----------------------")
check_num("Y", DF$Y)
print("-----------------------")
check_num("OBJECTID", DF$OBJECTID)
print("-----------------------")
check_num("ID", DF$ID)
print("-----------------------")
check_num("ADDR_ID", DF$ADDR_ID)
print("-----------------------")

check_char("TYPES", DF$TYPES)
print("-----------------------")
check_char("STATUS", DF$STATUS)
print("-----------------------")
check_char("STREET_NUM", DF$STREET_NUM)
check_notnum("STREET_NUM", DF$STREET_NUM)
print("-----------------------")

check_char("FRACTION", DF$FRACTION)
print("-----------------------")
check_char("PREFIX", DF$PREFIX)
print("-----------------------")
check_char("STREET_NAME", DF$STREET_NAME)
print("-----------------------")
check_char("SUFFIX", DF$SUFFIX)
print("-----------------------")
check_char("STREET_TYPE", DF$STREET_TYPE)
print("-----------------------")
check_char("STATE", DF$STATE)
print("-----------------------")
check_char("CITY", DF$CITY)
print("-----------------------")
check_char("ZIPCODE", DF$ZIPCODE)
check_notnum("ZIPCODE", DF$ZIPCODE)
print("-----------------------")
check_num("X_COORD", DF$X_COORD)
print("-----------------------")
check_num("Y_COORD", DF$Y_COORD)
print("-----------------------")
check_char("LOT", DF$LOT)
print("-----------------------")
check_char("BLOCK", DF$BLOCK)
print("-----------------------")
check_char("SOURCES", DF$SOURCES)
print("-----------------------")

```

## Data Observations

X and Y seem more reliable than X_COORD and Y_COORD. The range is correct, and there are no NA's. But do they differ?

OBJECTID looks good - the range more than covers the number of records, and no NA's. Are they unique?

ID has lots of NA's. Not sure what it is for.

Not sure what ADDR_ID is, but no NA's.

TYPES possibly useful, but largely NA dominated. 90% NA.

STATUS seems important, no NA's. Need to figure out what it means.

STREET_NUM has only 1 NA (good!), but almost 10,000 entries with an appended character string like "A" or "#1".

FRACTION is all over the map. Probably not useful.

PREFIX has issues. Case problems, and what is "C"?

STREET_NAME is good - no NA's.

SUFFIX is okay except for "Y" and "w".

STREET_TYPE is a problem. Too many. 109 street types? Really?

STATE has one NA. Seriously?

CITY has a lot of entries - 46! But only 2 NA's.

ZIPCODE: no NA's but 14 "7737*".

X_COORD, Y_COORD range wrong, needs further checking.

LOT don't know what it is, but doesn't look useful, to me.

BLOCK is NA about half the time, but appears to designate blocks when present.

SOURCES nearly always present, but not sure how I would use it.

Rest of the fields are internal things like date updated, who did the update, etc.

##  Data cleanup

Let's now go through and clean up the data. I'll just delete records which are unrecoverable (bad zipcode, street number NA, street number not a number? )

Also look at other issues that the summaries uncovered.

```{r cleaning one}

# drop fields I don't care about

DF_work <- DF %>% select(X, Y, OBJECTID, TYPES, STATUS,
                         STREET_NUM, PREFIX, STREET_NAME,
                         SUFFIX, STREET_TYPE, CITY,
                         ZIPCODE, X_COORD, Y_COORD, BLOCK)

# eliminate City, Street_number with NA

DF_work <- DF_work %>% filter(CITY!="NA", STREET_NUM!="NA")

# eliminate non-numeric zips

DF_work <- DF_work %>% filter(!grepl("\\D", ZIPCODE))


```

##  Look at coordinates

Let's look at X,Y vs X_COORD and Y_COORD. How different are they?

```{r Coordinatefest}

DF_work <- 
  DF_work %>% 
  filter(!is.na(X_COORD), !is.na(Y_COORD)) 
  
  DF_work %>% 
  mutate(xdiff=X-X_COORD, ydiff=Y-Y_COORD) %>% 
  select(X, Y, xdiff, ydiff) %>% 
  ggplot() +
    geom_histogram(aes(x = xdiff), fill = "red", alpha = 0.2) + 
    geom_histogram(aes(x = ydiff), fill = "blue", alpha = 0.2) 

  DF_work %>% 
  ggplot() +
    geom_histogram(aes(x = X_COORD), fill = "red", alpha = 0.2) + 
    geom_histogram(aes(x = Y_COORD), fill = "blue", alpha = 0.2) 
```

I see. X_COORD and Y_COORD are actual projected X,Y values, probably Lambert, while X,Y are actually lat, long values. I'll keep the projected coordinates for now. But delete the NA's.

## Objectid - unique?

```{r objectid}

n_distinct(DF_work$OBJECTID)
nrow(DF_work)

```

Yep. Unique. A very useful field.

## Status

Let's count up each status

```{r status counts}

DF_work %>% group_by(STATUS) %>% tally(sort=TRUE)

```

What do they mean?

COH Permanent, Center Point, and County are all good addresses. PRE means preliminary - probably will be made one of the first three, later. Abandon means used to be a valid address, but no longer is. For example, 2050 Main might have the building razed and replaced with two now at 2050A and 2050B. 2050 gets abandoned.

UTA - no clue. Seems to be valid, but not tied to a particular structure.

Reverse Geocode - Not sure, suspect it means "interpolated address".

Out of Range - really means out of sequence, e.g., 5,7,4,9 4 would be out of range. Drop these if doing any interpolation!

## STREET_NUM

What to do about those annoying extras added to the street numbers, like "A" or "#5"? Since my ultimate goal is to geocode by block range,
all I need to calculate is the block range, and something approximating
the center of the block. Should I use the average location, the median, or perhaps the midpoint between the min and max? I think initially I might calculate all three and compare, just to see how they each work. For all of these, I can drop the non-numeric and it will affect nothing. So that seems to be the answer.

```{r cleanup street number}

# remove anything following numerics that start with a non-numeric

DF_work %>% mutate(STREET_NUM=str_extract(STREET_NUM, "^\\d+")) -> 
  DF_work

check_char("STREET_NUM", DF_work$STREET_NUM)
check_notnum("STREET_NUM", DF_work$STREET_NUM)

# Make STREET_NUM numeric to ease later calculations

DF_work$STREET_NUM <- as.numeric(DF_work$STREET_NUM)

```

