---
title: "Zipcodes"
author: "Alan Jackson"
date: "1/22/2020"
output: html_document
---

```{r setup, include=FALSE}

options(stringsAsFactors = FALSE)
library(dplyr)
require(rgdal)
library(sf)

googlecrs <- 4326

path <- "/home/ajackson/Rprojects/Geocoding"

knitr::opts_chunk$set(echo = TRUE)
```

##  Read in COH file

File downloaded from city of Houston
https://cohgis-mycity.opendata.arcgis.com/datasets/coh-zipcode

Hopefully higher quality than the Houston-Galveston Council data.

Nope. Polygons actually overlap, in many places.

```{r read file}

fname <- paste0(path,"/Zipcodes/COH_ZIPCODE.shp")

zip <- st_read(fname)

#Reading layer `COH_ZIPCODE' from data source `/home/ajackson/~/projects/Geocoding/Zipcodes/COH_ZIPCODE.shp' using driver `ESRI Shapefile'
#Simple feature collection with 213 features and 12 fields
#geometry type:  MULTIPOLYGON
#dimension:      XY
#bbox:           xmin: -96.4575 ymin: 28.85938 xmax: -94.35424 ymax: 30.6692
#epsg (SRID):    4326
#proj4string:    +proj=longlat +datum=WGS84 +no_defs

# View the feature class
plot(zip)

# Drop unneeded stuff

zip <- zip %>% 
  select(-c(CREATION_U, DATE_CREAT, DATE_MODIF, DATE_POSTE, LAST_USER, SYS_ID, GlobalID))

# Check

z <- st_make_valid(zip)

inter <- st_intersection(z) %>% filter(n.overlaps > 1)
plot(inter %>% select(ZIP_CODE))

# Save

saveRDS(zip, paste0(path, "/Zipcode_Polygons.rds"))

```

##   Let's try census bureau file

https://www.census.gov/programs-surveys/geography/guidance/geo-areas/zctas.html

Hmmm... a couple of issues. This file is for the entire country, and
does not (so far I can see) contain state or county codes, to allow me
to easily subset it.
Additionally, it is ZCTA polygons, not Zipcode polygons, so it will
give the wrong zipcode sometimes.

```{r census zcta file}

fname <- paste0(path,"/Zipcodes/cb_2018_us_zcta510_500k.shp")

zip <- st_read(fname)

# Reading layer `cb_2018_us_zcta510_500k' from data source `/home/ajackson/~/projects/Geocoding/Zipcodes/cb_2018_us_zcta510_500k.shp' using driver `ESRI Shapefile'
# Simple feature collection with 33144 features and 5 fields
# geometry type:  MULTIPOLYGON
# dimension:      XY
# bbox:           xmin: -176.6847 ymin: -14.37374 xmax: 145.8304 ymax: 71.34122
# epsg (SRID):    4269
# proj4string:    +proj=longlat +datum=NAD83 +no_defs

plot(zip)

```

##  Found a newer? file called zipcode-generalized.zip from COH

Not good, full of overlaps

```{r generalized zipcodes}

fname <- paste0(path,"/Zipcodes/ZIPCODE_GENERALIZED.shp")

zip <- st_read(fname)

# Reading layer `ZIPCODE_GENERALIZED' from data source `/home/ajackson/~/projects/Geocoding/Zipcodes/ZIPCODE_GENERALIZED.shp' using driver `ESRI Shapefile'
# Simple feature collection with 185 features and 10 fields
# geometry type:  POLYGON
# dimension:      XY
# bbox:           xmin: 2856133 ymin: 13644660 xmax: 3320975 ymax: 14138760
# epsg (SRID):    NA
# proj4string:    +proj=lcc +lat_1=28.38333333333333 +lat_2=30.28333333333334 +lat_0=27.83333333333333 +lon_0=-99 +x_0=600000 +y_0=3999999.999999999 +datum=NAD83 +units=us-ft +no_defs

# View the feature class
plot(zip)

# Drop unneeded stuff

zip <- zip %>% 
  select(-c(CREATION_U, DATE_CREAT, DATE_MODIF, DATE_POSTE, LAST_USER, SYS_ID, GlobalID))

# Check

z <- st_make_valid(zip)

inter <- st_intersection(z) %>% filter(n.overlaps > 1)
plot(inter %>% select(ZCTA))



```

## Another census tiger file - does it have zipcodes?

Nope, ZCTA's

```{r census tiger}

fname <- paste0(path,"/Zipcodes/tl_2018_48201_faces.shp")

zip <- st_read(fname)

# Reading layer `ZIPCODE_GENERALIZED' from data source `/home/ajackson/~/projects/Geocoding/Zipcodes/ZIPCODE_GENERALIZED.shp' using driver `ESRI Shapefile'
# Simple feature collection with 185 features and 10 fields
# geometry type:  POLYGON
# dimension:      XY
# bbox:           xmin: 2856133 ymin: 13644660 xmax: 3320975 ymax: 14138760
# epsg (SRID):    NA
# proj4string:    +proj=lcc +lat_1=28.38333333333333 +lat_2=30.28333333333334 +lat_0=27.83333333333333 +lon_0=-99 +x_0=600000 +y_0=3999999.999999999 +datum=NAD83 +units=us-ft +no_defs

# View the feature class
plot(zip)

# Drop unneeded stuff

zip <- zip %>% 
  select(-c(CREATION_U, DATE_CREAT, DATE_MODIF, DATE_POSTE, LAST_USER, SYS_ID, GlobalID))

# Check

z <- st_make_valid(zip)

inter <- st_intersection(z) %>% filter(n.overlaps > 1)
plot(inter %>% select(ZCTA))




```

##  ESRI has a Layer Package file that may work

This looks like we have a winner. All I need do is figure out how to 
limit it to the Houston area.

```{r layer package}

fgdb <- "/home/ajackson/Rprojects/Geocoding/Zipcodes/esridata/v10/zip_poly.gdb"

# Read the feature class
zipdata2 <- st_read(fgdb) %>% filter(STATE=="TX")

# Reading layer `zip_poly' from data source `/home/ajackson/~/projects/Geocoding/Zipcodes/esridata/v10/zip_poly.gdb' using driver `OpenFileGDB'
# Simple feature collection with 30924 features and 8 fields
# geometry type:  MULTIPOLYGON
# dimension:      XY
# bbox:           xmin: -179.1473 ymin: 13.23419 xmax: 179.7785 ymax: 71.39048
# epsg (SRID):    4326
# proj4string:    +proj=longlat +datum=WGS84 +no_defs
# View the feature class

plot(zipdata2)

#   Big polygon to grab Houston area
Houston <- st_make_grid(z, cellsize = c(diff(st_bbox(z)[c(1, 3)]),
                                        diff(st_bbox(z)[c(2, 4)])),
                           offset = st_bbox(z)[c("xmin", "ymin")],
                           n = 1, crs = st_crs(z),
                           what = "polygons", square = TRUE)

Houston <- st_bbox(z) %>% t_make_grid()

#   Instead lets use the list of zips in COH file to filter out the
#   desired zips in the state file.

HoustonCodes <- append(as.character(z$ZIP_CODE),c("77316",
                                                  "77318",
                                                  "77328"))
  
zips <-  zipdata2 %>% 
  filter(ZIP_CODE %in% HoustonCodes) %>% 
  select(-c(PO_NAME, STATE, POPULATION, POP_SQMI, SQMI))

plot(zips)

saveRDS(zips, paste0(path, "/Zipcode_Polygons.rds"))

```

